A survey of HTTP caching implementations on the open Semantic Web

### 2015-03-11 sanity/paper1.tex
SPARQL evaluation with cache
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@1056 43ef1190-90fd-4dd7-a769-d0121f02b80e

Furthermore, by using similarity measures, like those discussed in

>>>>

Furthermore, by using similarity measures, like those discussed in
\cite{dividino2013following}, proxies can proactively prefetch data
into a cache to help answer queries. A cost model that takes into
account several data access methods, those described by
\cite{hogan2014paths} as well as  the novel work in \cite{ldf1} may be
a key ingredient in enabling efficient SPARQL evaluation on the Web.
